The Error Estimate of Short-Range Force Calculation in the Inhomogeneous Molecular Systems

### 2012-07-25 shortRange.inhomo/alltext/pubilsh.pre/resubmit/main.tex
finish response

{ One possible way to avoid the cut-off difficulty is to
  modify the short-range interaction by a shifting approach: inside a
  certain radius the original interaction is kept, while outside it the
  interaction is screened by a shift function, so that it goes to
  zero smoothly and rapidly. The amount of shifting is minor in most cases,
  however, it actually changes the way of
  modeling molecules. For example, it
  has been shown that shifting the dispersion remarkably changes the
  phase diagram of the Lennard-Jones system~\cite{smit1992phase}.
  Since the dispersion term 
  can be derived by quantum mechanical arguments, and has the physical
  reality, the unshifted interaction is
  preferred and investigated by most studies
  (see e.g. Ref.~\cite{potoff1998critical, perez2006critical}).
  % Shifting the direct part of the Ewald summation actually
  % violates the Coulomb's law in the way that depends on the
  % splitting parameter, so it should be treated carefully.
  % Here we would like to suggest treating the shifting approach
  % as a special case 
}
% In this paper, we focus on the systems in which
% atoms/particles are interacting via short-range interactions, because
% it is a good starting point of the study of more complex systems, for
% example, the systems with long-range electrostatic interactions.  The
% simulation results in the inhomogeneous systems are found to depend on
% a number of factors of treating the short-range interaction in the
% simulation. For example, the way of calculating the short-range
% interaction (simple cut-off method or Ewald
% summation)~\cite{karasawa1989acceleration, lopez2002thermodynamic,
%   lopez2006liquid, shi2006molecular, ismail2007application}, the
% cut-off radius~\cite{trokhymchuk1999computer, duque2004some,
%   shen2007comparative}, the way of long-range
% correction~\cite{guo1997long, mecke1997molecular, janecek2006long,
%   goujon2004monte} and the size and shape of the simulation
% box~\cite{chen1995area, orea2005oscillatory, biscay2009calculation}.
% It should be noticed that the physical properties are the nature of
% the system, and should NOT depend on the details of the interaction
% calculation.

@@

To show the
effectiveness of the error estimate and the proposed methods, two
systems are tested: the liquid-vapor equilibrium for equilibrium
properties, and the colliding nanoscale clusters for dynamical
properties.{
  In these example, we investigate the Lennard-Jones interaction, which
  is one of the most widely used in molecular simulations.
  However, the error estimate,
  the adaptive cut-off and long-range correction methods
  are not restricted to the Lennard-Jones: it can
  be applied to other types of short-range interactions without 
  difficulty, such as
  Buckingham, the direct part of Ewald family algorithms~\cite{ewald1921die, darden1993pme, essmann1995spm, deserno1998mue1}, etc..  
  We want to stress that the main contribution and the research interest is the
  quantitative study of the force computation error by cutting-off
  the short-range interaction.
  The examples, which are comparatively simple and ideal,
  are used only for testing the validity of the error
  estimate and the proposed methods,
  and demonstrating the role of different errors in the simulations.
  The error study in more realistic systems requires the
  estimates of the electrostatic interaction,
  which are calculated by the long-range algorithms, such as
  PME~\cite{darden1993pme}, SPME~\cite{essmann1995spm},
  P3M~\cite{deserno1998mue1}, etc..
  The space of the present paper is not enough for
  these algorithms, so they will be delivered in the future work.
}
% Finally, conclusions are given in section
% \ref{sec:conclusion}.

% The error estimate of long-range algorithms, for example the Ewald
% family method~\cite{ewald1921die, hockney1988computer,
%   deserno1998mue1, darden1993pme, essmann1995spm} and the fast
% multipole method~\cite{greengard1987fast}, has been well developped in
% the past 20 years ~\cite{hummer1995numerical, kolafa1992cutoff,
%   petersen1995accuracy, deserno1998mue2, wang2010optimizing,
%   dachsel2009error}.

@@

In this paper, for simplicity,
we will consider one-component systems, but
% we only consider the single-component system. Because
% this assumption simplifies the discussion, and
the error estimate for
the one-component system can be straightforwardly extended to the
multi-component systems.  We consider
the force error in the present paper, because the
applications are based on molecular dynamics simulations.
% Since the error estimate developed for the one-component system can be
% directly extended to multi-component system without substantial
% difficulty, the discussion in this paper will focus on one-component
% system for symplicity. 
Suppose the system is composed by $N$ identical particles located at
$\v r_1, \v r_2, \cdots, \v r_N$ with periodic boundary condition.
These particles are interacting via a short-range pairwise interaction
$u(\v r)$ with a cut-off radius $r_c > 0$.
The corresponding force is
denoted by $\v f(\v r)$. 
Most short-range interactions satisfy $\vert
u(r)\vert\leq C r^{-m}$, $m>3$, which guarantees an absolute convergence of the
energy.
Throughout the paper, the only assumptions made on the interaction are:
(1) the interaction is short-ranged and (2)
it is calculated by the cut-off method.
Therefore, our approach works for a large group of widely used interactions, 
for example, the Lennard-Jones interaction, the Buckingham interaction,
the direct part of Ewald family algorithms, and so forth.
% An infinite cut-off radius will lead to
% a precise calculation of interaction, but it is impractical.
% The error of computing interaction is mainly introduced by a finit
% value of the cut-off radius.

@@

% In Fig. \ref{fig:tmp1}, the testing system containing $N=16000$
% standard Lennard-Jones particles is set up in a tube with periodic
% boundary condition. The liquid droplet (in the middle of the tube) is
% in equilibrium with the surrounding vapor environment. The red line in
% the Fig. \ref{fig:tmp2} denotes the density profile (on direction $x$)
% of this inhomogeneous system. The green square denotes the real RMS
% force error distribution. It is clear that the error form two peaks in
% the interfacial region, which is much higher than the relative
% constant error of the bulk liquid and the bulk vapor. The dashed and
% the dotted blue line are the estimated homogeneity and inhomogeneity
% errors, and the solid blue line is the sum. In the bulk region, the
% homogeneity error dominates while in the interfacial region, the
% inhomogeneity error dominates. The esitmated error matches perfactly
% with the real error at the interfacial region, but presents
% overestimation in the bulk regions. The overestimation probably stems
% from the neglection of the correlation error in \eqref{eqn:tmp5}.

@@

% Since inhomogeneity error dominate the
% force error of the system, such a big cutoff radius is a waste in the
% bulk liquid and vapor regions. One possible way is to use adapt
% cut-off radius according to the error distribution, so that larger
% cut-off radii are used in the interfacial region while smaller cut-off
% radii are used in the bulk regions.  More precisely, the aim of the
% adaptive cut-off method is to equivalently distributed the force error
% over the simulation region.

@@

% This
% means the force error is a combination of a homogeneous contribution,
% an inhomogeneous contribution and a correlational contribution. The
% inhomogeneous force can be applied as a correction to the error:
% \begin{align}\label{eqn:tmp7}
%   \v F_{\textrm{inhomo}} = \int_{\mathbb R^3}\v F^c(\v r - \v r')\rho(\v r')\,\d d\v r'
% \end{align}

@@

% \textrm{Var}[\Delta\v F_{\textrm{corr}}(\v r)] =

% This means if we correct the computed force by the mean of the error
% force, namely applying to each particle $\tilde{\v F}^c(\v r) =
% \tilde{\v F}(\v r) - \langle\Delta\v F(\v r)\rangle$ instead of
% $\tilde{\v F}(\v r)$.

\subsection{Long-range pressure correction}
% By the cut-off method, the system lost the pressure contribution from
% the particles outside the cut-off radius.  In the homogeneous systems,
% the distribution of particles is assumed to be uniform outside the
% cut-off radius, and the pressure correction is calculated by
% integrating the virial from the cut-off to infinity.

% In the inhomogeneous systems, the previous idea does not
% work. Instead, the pressure correction of the system are:

The pressure contribution outside the cut-off radius can be expressed
by:
\begin{align}
  \v P^c &= \frac1{V} \bigg\langle \sum_{i\neq j}\,\frac12\, (\v r_i - \v r_j) \otimes \v f^c(\v r_i - \v r_j) \bigg\rangle
\end{align}
For simplicity, we denote $\frac{1}{2V}\v r\otimes\v f^c$ by $\v
K_{\textrm{P}}$, therefore,
% For simplicity, let us consider the general form the the corrections:
% \begin{align}
%   Q = \bigg\langle \sum_{i\neq j} K(\v r_i - \v r_j) \bigg\rangle
% \end{align}
% For the pressure correction, $K$ is replaced by $\frac{1}{2V}\v
% r\otimes\v f^c$.  By using \eqref{eqn:tmp7}, we have
\begin{align}\nonumber
  \v P^c
  &= \bigg\langle \sum_{i\neq j} \v K_{\textrm{P}}(\v r_i - \v r_j) \bigg\rangle\\\nonumber
  & = \int_{\mathbb R^3\times\mathbb R^3}
  \v K_{\textrm{P}}(\v r' - \v r'') \rho(\v r', \v r'') \d d\v r'\d d\v r'' \\\nonumber
  & = \int_{\mathbb R^3\times\mathbb R^3}
  \v K_{\textrm{P}}(\v r' - \v r'')
  \big[
  \rho(\v r') \rho(\v r'') + C(\v r', \v r'')
  \big]
  \d d\v r'\d d\v r''
\end{align}
Assuming the correlation term $C(\v r', \v r'')$ vanishes, then
\begin{align} \nonumber
  \v P^c
  & = \int_{\mathbb R^3\times\mathbb R^3} \v K_{\textrm{P}}(\v r' - \v r'')
  \rho(\v r') \rho(\v r'') 
  \d d\v r'\d d\v r'' \\
  & = \int_{\mathbb R^3}
  \Big[
  \int_{\mathbb R^3} \v K_{\textrm{P}}(\v r' - \v r'') \rho(\v r'')\,\d d\v r''
  \Big]
  \rho(\v r')\,\d d\v r'
\end{align}
The Fourier transform of the convolution $\int \v K_{\textrm{P}}(\v r'
- \v r'') \rho(\v r'')\,\d d\v r''$ is identical to the product $\hat
{\v K}_{\textrm{P}}(\v k)\,\hat \rho(\v k)$.
Assuming the isotropicity of the short-range interaction,
the $\alpha\beta$ component of $\v K_{\textrm{P}}$ can be written as
\begin{align}
  \{\v K_{\textrm{P}}\}_{\alpha\beta}
  = \frac1{2V}\{\v r\otimes\v f^c\}_{\alpha\beta}
  = \frac1{2V} r_\alpha r_\beta \,G^c(r)
  \qquad \alpha, \beta = 1, 2, 3,
\end{align}
where $G^c(r) = [u^c(r)]'/r$ is isotropic.  We list
here without proving the Fourier transform of these terms:
\begin{align}
  [\,r_1r_1\,G^c(r)\,]^{\wedge} 
  =\,& 
  \int_{r_c}^\infty \d dr\, r^4 G^c(r)\,
  \pi \sqrt{ \frac1{kr} }\,
  \Big[\,
  \frac23\,J_{\frac12}(2\pi kr) -
  \big(\,
  \frac13 -
  \cos^2\Phi +
  \sin^2\Phi\cos2\Theta
  \big)\, J_{\frac52}(2\pi kr)
  \,\Big] \\
  [\,r_2 r_2\,G^c(r)\,]^{\wedge} 
  =\,& 
  \int_{r_c}^\infty \d dr\, r^4 G^c(r)\,
  \pi \sqrt{ \frac1{kr} }\,
  \Big[\,
  \frac23\,J_{\frac12}(2\pi kr) -
  \big(\,
  \frac13 -
  \cos^2\Phi -
  \sin^2\Phi\cos2\Theta
  \big)\, J_{\frac52}(2\pi kr)
  \,\Big]   \\
  [\,r_3 r_3\,G^c(r)\,]^{\wedge} 
  =\,& 
  \int_{r_c}^\infty \d dr\: \,r^4 G^c(r)\,\pi\,
  \sqrt{ \frac1{kr} }\,
  \Big[\,
  \frac23 J_{\frac12}(2\pi kr) +
  \big(\,
  \frac23 - 2\cos^2\Phi
  \big)
  J_{\frac52}(2\pi kr)
  \,\Big]\\
  [\,r_1 r_2\,G^c(r)\,]^{\wedge} 
  =\,& -
  \int_{r_c}^\infty
  \d dr\,
  r^4G^c(r)\,\pi\,
  \sqrt{\frac1{kr}}\:
  \sin^2\Phi\sin 2\Theta\,J_{\frac52}(2\pi kr)\\
  [\,r_1 r_3\,G^c(r)\,]^{\wedge} 
  =\,& -
  \int_{r_c}^\infty
  \d dr\,
  r^4G^c(r)\,\pi\,
  \sqrt{\frac1{kr}}\:
  \sin2\Phi\cos\Theta\,J_{\frac52}(2\pi kr)\\
  [\,r_2 r_3\,G^c(r)\,]^{\wedge} 
  =\,& -
  \int_{r_c}^\infty
  \d dr\,
  r^4G^c(r)\,\pi\,
  \sqrt{\frac1{kr}}\:
  \sin2\Phi\sin\Theta\,J_{\frac52}(2\pi kr)
\end{align}
Where $(k, \Phi, \Theta)$ are the spherical coordinates of reciprocal
variable $\v k$, and $J_\nu(x)$ is the Bessel function of the first
kind.

@@

% The Fig. \ref{fig:tmp2} inspires us to develop the adaptive cut-off
% method: in the bulk regions, the error is much smaller, therefore, it
% is a waste to use the same cut-off radius as the interfacial
% regions.
As mentioned before, the key idea of the adaptive cut-off simulation
is to use smaller cut-off
radius in the bulk regions, so that the RMS force error is uniformly
distributed over the simulation region. In Fig. \ref{fig:tmp3}, we
present the adapted cut-off radius by a solid red line and all errors
by the same notations as in the Fig. \ref{fig:tmp2}. The control error
$\mathcal E^\ast_{\textrm{C}} = 0.0045$ is almost the same as the maximum
error in the uniform cut-off simulation with $r_c^\ast=7.5$.
{
  In the rest of the paper, when we mention that ``the cut-off of
  the adaptive cut-off method is $r_c^\ast$'', we mean the
  control error is the maximum error of a uniform cut-off simulation
  using that cut-off $r_c^\ast$. In all the cases considered by
  the present paper, the maximum of
  the adapted cut-off radius is almost the same as $r_c^\ast$,
  and is sometimes marginally larger (no more than $r_c^\textrm{step}$).
}
The
cut-off distribution is calculated every 20,000 time steps, and is
refined twice by Eqn.~\eqref{eqn:rc-refine}.
Due to this low cut-off redistribution frequency,
the extra cost of this adaptive method is only marginal
comparing with the total computational cost.
In the interfacial
regions, the same cut-off radius as the uniform cut-off simulation,
namely $7.5$, is used.  In the bulk
liquid and vapor regions, the cut-off radii are $4.75$ and $3.5$,
which reduce the computational cost
by a factor of 4 and 10, respectively.
The error is uniformly distributed, except in the
liquid region where the real error is somewhat lower.
In contrast with the uniform
cut-off case, i.e. Fig. \ref{fig:tmp2}, the error estimate for the
vapor region is very sharp.
The similar phenomenon is observed in
Ref.~\cite{wang2011}.
The same as the uniform cut-off simulation, the
homogeneity error dominates in the bulk regions, while the
inhomogeneity error dominates in the interfacial region.

@@

% Clearly the contribution of the inhomogeneity
% error is successfully removed, because the estimate of homogeneity
% error follows the real error perfectly in the interfacial regions.  In
% the bulk liquid region, the homogeneity error is slightly
% overestimated, which is the same as the uniform and adaptive cut-off
% simulations.

@@

% As mentioned before, form Fig. \ref{fig:tmp2}, the error dominates at
% the interfacial regions. The error estimate is sharp in these
% regions. While in the bulk regions, the error estimate is not sharp,
% but still acceptable. By the adapt cut-off radius MD, the resulting
% distribution (averaged on $y$ and $z$ directions) of cut-off radius is
% given in Fig. \ref{fig:tmp3}. In the interfacial regions, the cut-off
% radius is adapted to $r_c^\ast = 7.5$. In the bulk liquid and vapor
% regions, the cut-off radii are approximatly $5.0$ and $3.5$.  The
% resulting error distribution is ploted in FIg. \ref{fig:tmp4}. It is
% clear that the error is comparatively uniformly distributed in the
% space. The estimate inhomogeneity error is also dominant at the
% interfacial region, while the homogeneous error dominants in the bulk
% regions.  Since the computational cost is proportional to $r_c^3$,
% comparing with a simulation using uniform cut-off radius $7.5$, the
% adaptive cut-off simulation saves 3.4 times and 9.8 times
% computational cost, respectively. In total, the adaptive cut-off
% radius method save 50\% of the computational cost.

% We test the uniform and adaptive cut-off methods as well as the
% correction force method in the mentioned liquid vapor equilibrium
% system.

To test the effectiveness of the proposed adaptive cut-off and
long-range force correction methods, we measure the liquid-vapor
equilibrium density and the surface tension defined by
\begin{align}
  \gamma = \frac12 \int_{L_x}
  \bigg[\,
  p_x(x) - \frac{p_y(x) + p_z(x)}{2}
  \,\bigg]
  \,\d dx.
\end{align}
Where $p_x$, $p_y$ and $p_z$ are $x$, $y$ and $z$ component of the
pressure. The convergence of the properties of interest with respect
to the cut-off radius is considered.
% For the adaptive cut-off
% simulation, the ``cut-off radius'' means the largest cut-off radius
% used in the simulation region.

\begin{figure}
  \centering
  \includegraphics[width=0.49\textwidth]{t0.85.gas.eps} 
  \includegraphics[width=0.49\textwidth]{t0.85.liquid.eps} 
  \caption{(Color online)
    $T^\ast = 0.85$. The convergence of the equilibrium gas and
    liquid densities with respect to the cut-off radius. All densities
    are compared with the reference value (black solid line), namely,
    the liquid and vapor densities measured with a uniform cut-off
    radius $r_c^\ast=13$. The gray region denotes the statistical
    uncertainty of the reference value.  This figure presents the
    results of three methods,
    namely the uniform cut-off (URC) in red (middle gray), the
    adaptive cut-off (ARC) in green (light gray)
    and the force correction (LFC) method in blue (dark gray).
    The cut-off of
    the adaptive cut-off method is $r_c^\ast$ means its
    control error is the maximum error of a uniform cut-off simulation
    using that cut-off $r_c^\ast$.
    Under this setting,  the maximum 
    cut-off radius of the adaptive cut-off method is the same as,
    or sometimes marginally larger  than
    $r_c^\ast$ (no more than $r_c^{\textrm{{step}}}$).
  }
  \label{fig:tmp5}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.49\textwidth]{tension.t0.85.eps} 
  \caption{(Color online)
    $T^\ast = 0.85$. The convergence of the surface tension
    with respect to the cut-off radius.  This figure presents the
    results of three methods,
    namely the uniform cut-off (URC) in red (middle gray),
    the adaptive cut-off (ARC) in green (light gray)
    and the long-range force correction (LFC) method in blue (dark gray).
    The results with and without long-range pressure
    correction (LPC) are shown together for comparison. The reference
    surface tension, shown by the solid black line, is measured by the
    uniform cut-off method with $r_c^\ast=13$ using LPC.
    The cut-off of
    the adaptive cut-off method is $r_c^\ast$ means its
    control error is the maximum error of a uniform cut-off simulation
    using that cut-off $r_c^\ast$.
    Under this setting,  the maximum 
    cut-off radius of the adaptive cut-off method is the same as,
    or sometimes marginally larger  than
    $r_c^\ast$ (no more than $r_c^{\textrm{{step}}}$).
    % This setting leads to a maximum 
    % cut-off radius that is almost the same as $r_c^\ast$.
  }
  \label{fig:tmp6}
\end{figure}

@@

% In the higher
% temperature cases, the thermodynamic flucuation of the system is
% stronger. Therefore, the meansurement of densities and surface tension
% are less accurate.
% At $T^\ast = 0.70$, the gas
% density converges much faster than the liquid density, while at
% $T^\ast = 1.20$, the gas and liquid densities almost converges at the
% same speed, see Fig. \ref{fig:tmp5}.

@@

% With the
% same cut-off radius, the computational cost of the force correction is
% nearly the same as the uniform cut-off methods, see
% Tab. \ref{tab:tmp1}, and at the same time, the force accuracy is more
% than one order of maganitude better.

% However, the maximum
% force error of the force correction method is reduced by about one
% order of maganitude.
% We also observe that the liquid densities are systemetically higher
% than the reference results. This fact will be discussed latter by
% comparing with literature results.

The surface tension result of the force correction without pressure
correction is only slightly better than the uniform and adaptive
cut-off methods without pressure correction (see Fig. \ref{fig:tmp6}).
With the long-range pressure correction, the convergence of the
surface tension of all methods are largely improved.  The force
correction method converges at $r_c^\ast = 3.5$, and the
uniform/adaptive cut-off methods converge at $r_c^\ast = 5.0\sim 6.0$.  The
discrepancy between the corrected and uncorrected tension is the
amount of the correction, which decreases with the increasing cut-off
radius. {
  However, even at a rather large cut-off of $r_c^\ast=10$,
  the amount of the correction is still not negligible, which tells the users
  that the uncorrected tension calculation is far from convergence.
  % the extend of which is shown by the
  % the amount of the correction calculated by the pressure correction method.
}  
% However, even at $r_c^\ast=10$, this correction is not
% negligible, so it is very important for the precise surface tension
% calculation.

>>>>

{ One possible way to avoid the cut-off difficulty is to
  modify the short-range interaction by a shifting approach: inside a
  certain radius the original interaction is kept, while outside it the
  interaction is screened by a shift function, so that it goes to
  zero smoothly and rapidly. The amount of shifting is minor in most cases,
  however, it actually changes the way of
  modeling molecules. For example, it
  has been shown that shifting the dispersion remarkably changes the
  phase diagram of the Lennard-Jones system~\cite{smit1992phase}.
  Since the dispersion term 
  can be derived by quantum mechanical arguments, and has the physical
  reality, the unshifted interaction is
  preferred and investigated by most studies
  (see e.g. Ref.~\cite{potoff1998critical, perez2006critical}).
}

@@

To show the
effectiveness of the error estimate and the proposed methods, two
systems are tested: the liquid-vapor equilibrium for equilibrium
properties, and the colliding nanoscale clusters for dynamical
properties.{
  In these example, we investigate the Lennard-Jones interaction, which
  is one of the most widely used in molecular simulations.
  However, the error estimate,
  the adaptive cut-off and long-range correction methods
  are not restricted to the Lennard-Jones: it can
  be applied to other types of short-range interactions without 
  difficulty, such as
  Buckingham, the direct part of Ewald family algorithms~\cite{ewald1921die, darden1993pme, essmann1995spm, deserno1998mue1}, etc..  
  We want to stress that the main contribution and the research interest is the
  quantitative study of the force computation error by cutting-off
  the short-range interaction.
  The examples, which are comparatively simple and ideal,
  are used only for testing the validity of the error
  estimate and the proposed methods,
  and demonstrating the role of different errors in the simulations.
  The error study in more realistic systems requires the
  estimates of the electrostatic interaction,
  which are calculated by the long-range algorithms, such as
  PME~\cite{darden1993pme}, SPME~\cite{essmann1995spm},
  P3M~\cite{deserno1998mue1}, etc..
  The space of the present paper is not enough for
  these algorithms, so they will be delivered in the future work.
}

@@

In this paper, for simplicity,
we will consider one-component systems, but
the error estimate for
the one-component system can be straightforwardly extended to the
multi-component systems.  We consider
the force error in the present paper, because the
applications are based on molecular dynamics simulations.
Suppose the system is composed by $N$ identical particles located at
$\v r_1, \v r_2, \cdots, \v r_N$ with periodic boundary condition.
These particles are interacting via a short-range pairwise interaction
$u(\v r)$ with a cut-off radius $r_c > 0$.
The corresponding force is
denoted by $\v f(\v r)$. 
Most short-range interactions satisfy $\vert
u(r)\vert\leq C r^{-m}$, $m>3$, which guarantees an absolute convergence of the
energy.
Throughout the paper, the only assumptions made on the interaction are:
(1) the interaction is short-ranged and (2)
it is calculated by the cut-off method.
Therefore, our approach works for a large group of widely used interactions, 
for example, the Lennard-Jones interaction, the Buckingham interaction,
the direct part of Ewald family algorithms, and so forth.

@@

@@

@@

@@

\subsection{Long-range pressure correction}

The pressure contribution outside the cut-off radius can be expressed
by:
\begin{align}
  \v P^c &= \frac1{V} \bigg\langle \sum_{i\neq j}\,\frac12\, (\v r_i - \v r_j) \otimes \v f^c(\v r_i - \v r_j) \bigg\rangle
\end{align}
For simplicity, we denote $\frac{1}{2V}\v r\otimes\v f^c$ by $\v
K_{\textrm{P}}$, therefore,
\begin{align}\nonumber
  \v P^c
  &= \bigg\langle \sum_{i\neq j} \v K_{\textrm{P}}(\v r_i - \v r_j) \bigg\rangle\\\nonumber
  & = \int_{\mathbb R^3\times\mathbb R^3}
  \v K_{\textrm{P}}(\v r' - \v r'') \rho(\v r', \v r'') \d d\v r'\d d\v r'' \\\nonumber
  & = \int_{\mathbb R^3\times\mathbb R^3}
  \v K_{\textrm{P}}(\v r' - \v r'')
  \big[
  \rho(\v r') \rho(\v r'') + C(\v r', \v r'')
  \big]
  \d d\v r'\d d\v r''
\end{align}
Assuming the correlation term $C(\v r', \v r'')$ vanishes, then
\begin{align} \nonumber
  \v P^c
  & = \int_{\mathbb R^3\times\mathbb R^3} \v K_{\textrm{P}}(\v r' - \v r'')
  \rho(\v r') \rho(\v r'') 
  \d d\v r'\d d\v r'' \\
  & = \int_{\mathbb R^3}
  \Big[
  \int_{\mathbb R^3} \v K_{\textrm{P}}(\v r' - \v r'') \rho(\v r'')\,\d d\v r''
  \Big]
  \rho(\v r')\,\d d\v r'
\end{align}
The Fourier transform of the convolution $\int \v K_{\textrm{P}}(\v r'
- \v r'') \rho(\v r'')\,\d d\v r''$ is identical to the product $\hat
{\v K}_{\textrm{P}}(\v k)\,\hat \rho(\v k)$.
Assuming the isotropicity of the short-range interaction,
the $\alpha\beta$ component of $\v K_{\textrm{P}}$ can be written as
\begin{align}
  \{\v K_{\textrm{P}}\}_{\alpha\beta}
  = \frac1{2V}\{\v r\otimes\v f^c\}_{\alpha\beta}
  = \frac1{2V} r_\alpha r_\beta \,G^c(r)
  \qquad \alpha, \beta = 1, 2, 3,
\end{align}
where $G^c(r) = [u^c(r)]'/r$ is isotropic.  We list
here without proving the Fourier transform of these terms:
\begin{align}
  [\,r_1r_1\,G^c(r)\,]^{\wedge} 
  =\,& 
  \int_{r_c}^\infty \d dr\, r^4 G^c(r)\,
  \pi \sqrt{ \frac1{kr} }\,
  \Big[\,
  \frac23\,J_{\frac12}(2\pi kr) -
  \big(\,
  \frac13 -
  \cos^2\Phi +
  \sin^2\Phi\cos2\Theta
  \big)\, J_{\frac52}(2\pi kr)
  \,\Big] \\
  [\,r_2 r_2\,G^c(r)\,]^{\wedge} 
  =\,& 
  \int_{r_c}^\infty \d dr\, r^4 G^c(r)\,
  \pi \sqrt{ \frac1{kr} }\,
  \Big[\,
  \frac23\,J_{\frac12}(2\pi kr) -
  \big(\,
  \frac13 -
  \cos^2\Phi -
  \sin^2\Phi\cos2\Theta
  \big)\, J_{\frac52}(2\pi kr)
  \,\Big]   \\
  [\,r_3 r_3\,G^c(r)\,]^{\wedge} 
  =\,& 
  \int_{r_c}^\infty \d dr\: \,r^4 G^c(r)\,\pi\,
  \sqrt{ \frac1{kr} }\,
  \Big[\,
  \frac23 J_{\frac12}(2\pi kr) +
  \big(\,
  \frac23 - 2\cos^2\Phi
  \big)
  J_{\frac52}(2\pi kr)
  \,\Big]\\
  [\,r_1 r_2\,G^c(r)\,]^{\wedge} 
  =\,& -
  \int_{r_c}^\infty
  \d dr\,
  r^4G^c(r)\,\pi\,
  \sqrt{\frac1{kr}}\:
  \sin^2\Phi\sin 2\Theta\,J_{\frac52}(2\pi kr)\\
  [\,r_1 r_3\,G^c(r)\,]^{\wedge} 
  =\,& -
  \int_{r_c}^\infty
  \d dr\,
  r^4G^c(r)\,\pi\,
  \sqrt{\frac1{kr}}\:
  \sin2\Phi\cos\Theta\,J_{\frac52}(2\pi kr)\\
  [\,r_2 r_3\,G^c(r)\,]^{\wedge} 
  =\,& -
  \int_{r_c}^\infty
  \d dr\,
  r^4G^c(r)\,\pi\,
  \sqrt{\frac1{kr}}\:
  \sin2\Phi\sin\Theta\,J_{\frac52}(2\pi kr)
\end{align}
Where $(k, \Phi, \Theta)$ are the spherical coordinates of reciprocal
variable $\v k$, and $J_\nu(x)$ is the Bessel function of the first
kind.

@@

As mentioned before, the key idea of the adaptive cut-off simulation
is to use smaller cut-off
radius in the bulk regions, so that the RMS force error is uniformly
distributed over the simulation region. In Fig. \ref{fig:tmp3}, we
present the adapted cut-off radius by a solid red line and all errors
by the same notations as in the Fig. \ref{fig:tmp2}. The control error
$\mathcal E^\ast_{\textrm{C}} = 0.0045$ is almost the same as the maximum
error in the uniform cut-off simulation with $r_c^\ast=7.5$.
{
  In the rest of the paper, when we mention that ``the cut-off of
  the adaptive cut-off method is $r_c^\ast$'', we mean the
  control error is the maximum error of a uniform cut-off simulation
  using that cut-off $r_c^\ast$. In all the cases considered by
  the present paper, the maximum of
  the adapted cut-off radius is almost the same as $r_c^\ast$,
  and is sometimes marginally larger (no more than $r_c^\textrm{step}$).
}
The
cut-off distribution is calculated every 20,000 time steps, and is
refined twice by Eqn.~\eqref{eqn:rc-refine}.
Due to this low cut-off redistribution frequency,
the extra cost of this adaptive method is only marginal
comparing with the total computational cost.
In the interfacial
regions, the same cut-off radius as the uniform cut-off simulation,
namely $7.5$, is used.  In the bulk
liquid and vapor regions, the cut-off radii are $4.75$ and $3.5$,
which reduce the computational cost
by a factor of 4 and 10, respectively.
The error is uniformly distributed, except in the
liquid region where the real error is somewhat lower.
In contrast with the uniform
cut-off case, i.e. Fig. \ref{fig:tmp2}, the error estimate for the
vapor region is very sharp.
The similar phenomenon is observed in
Ref.~\cite{wang2011}.
The same as the uniform cut-off simulation, the
homogeneity error dominates in the bulk regions, while the
inhomogeneity error dominates in the interfacial region.

@@

@@

To test the effectiveness of the proposed adaptive cut-off and
long-range force correction methods, we measure the liquid-vapor
equilibrium density and the surface tension defined by
\begin{align}
  \gamma = \frac12 \int_{L_x}
  \bigg[\,
  p_x(x) - \frac{p_y(x) + p_z(x)}{2}
  \,\bigg]
  \,\d dx.
\end{align}
Where $p_x$, $p_y$ and $p_z$ are $x$, $y$ and $z$ component of the
pressure. The convergence of the properties of interest with respect
to the cut-off radius is considered.

\begin{figure}
  \centering
  \includegraphics[width=0.49\textwidth]{t0.85.gas.eps} 
  \includegraphics[width=0.49\textwidth]{t0.85.liquid.eps} 
  \caption{(Color online)
    $T^\ast = 0.85$. The convergence of the equilibrium gas and
    liquid densities with respect to the cut-off radius. All densities
    are compared with the reference value (black solid line), namely,
    the liquid and vapor densities measured with a uniform cut-off
    radius $r_c^\ast=13$. The gray region denotes the statistical
    uncertainty of the reference value.  This figure presents the
    results of three methods,
    namely the uniform cut-off (URC) in red (middle gray), the
    adaptive cut-off (ARC) in green (light gray)
    and the force correction (LFC) method in blue (dark gray).
    ``The cut-off of
    the adaptive cut-off method is $r_c^\ast$'' means that the
    control error  $\mathcal E^\ast_{\textrm{C}}$
    is the same as the maximum error of a uniform cut-off simulation
    using $r_c^\ast$.
    Under this setting,  the maximum 
    cut-off radius of the adaptive cut-off method is the same as,
    or sometimes marginally larger  than
    $r_c^\ast$ (no more than $r_c^{\textrm{{step}}}$).
  }
  \label{fig:tmp5}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.49\textwidth]{tension.t0.85.eps} 
  \caption{(Color online)
    $T^\ast = 0.85$. The convergence of the surface tension
    with respect to the cut-off radius.  This figure presents the
    results of three methods,
    namely the uniform cut-off (URC) in red (middle gray),
    the adaptive cut-off (ARC) in green (light gray)
    and the long-range force correction (LFC) method in blue (dark gray).
    The results with and without long-range pressure
    correction (LPC) are shown together for comparison. The reference
    surface tension, shown by the solid black line, is measured by the
    uniform cut-off method with $r_c^\ast=13$ using LPC.
    ``The cut-off of
    the adaptive cut-off method is $r_c^\ast$'' means that the
    control error  $\mathcal E^\ast_{\textrm{C}}$
    is the same as the maximum error of a uniform cut-off simulation
    using $r_c^\ast$.
    Under this setting,  the maximum 
    cut-off radius of the adaptive cut-off method is the same as,
    or sometimes marginally larger  than
    $r_c^\ast$ (no more than $r_c^{\textrm{{step}}}$).
    % This setting leads to a maximum 
    % cut-off radius that is almost the same as $r_c^\ast$.
  }
  \label{fig:tmp6}
\end{figure}

@@

@@

The surface tension result of the force correction without pressure
correction is only slightly better than the uniform and adaptive
cut-off methods without pressure correction (see Fig. \ref{fig:tmp6}).
With the long-range pressure correction, the convergence of the
surface tension of all methods are largely improved.  The force
correction method converges at $r_c^\ast = 3.5$, and the
uniform/adaptive cut-off methods converge at $r_c^\ast = 5.0\sim 6.0$.  The
discrepancy between the corrected and uncorrected tension is the
amount of the correction, which decreases with the increasing cut-off
radius. {
  However, even at a rather large cut-off of $r_c^\ast=10$,
  the amount of the correction is still not negligible, which tells the users
  that the uncorrected tension calculation is far from convergence.
}

Comparing the results of the force correction method at $r_c^\ast =
3.5$ and uniform cut-off radius method at $r_c^\ast = 6.0$, the force
accuracy of the former method is a little worse than the latter (see
Tab. \ref{tab:tmp1}), but the equilibrium density accuracy is better than,
and surface tension is equally good (see
Fig. \ref{fig:tmp5} and \ref{fig:tmp6}).
Since the homogeneity error dominates in the former simulation and the
inhomogeneity error dominates in the latter, the above observation
indicates different natures of error play different roles in the
equilibrium densities.  The homogeneity error is actually the variation of the
corrected error force with its mean equal to zero (see
Eqn.~\eqref{eqn:mean-fcorr}). This implies that the corrected error
force may point to any direction with the same probability, and may self-cancel
in a long time average.  The inhomogeneity error,
in contrast, stems from the non-vanishing mean value of the error
force, which is always pointing to one certain direction (the opposite
direction of the density gradient), and has low  opportunity to be
self-canceled.
